%-----------CS Resume Template                                        -----------
%-----------Based on "Jack's Resume" (by Jake Gutierrez, MIT License) -----------
%-----------Modified by Shengyuan Lu (MIT License)                    -----------
%-----------GitHub: https://github.com/shengyuan-lu                   -----------
%-----------Linkedin: https://www.linkedin.com/in/shengyuan-lu/       -----------
  
\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[super]{nth}
\input{glyphtounicode}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Harrison Fisher} \\ \vspace{7pt}
    \small (707)908-6532 $ | $ 
    \href{Harrison.Fisher2018@gmail.com}{\underline{Harrison.Fisher2018@gmail.com}} $ | $ 
    \href{https://www.linkedin.com/in/harrison-fisher-cs/}{\underline{\faLinkedin \hspace{1pt} linkedin.com/in/harrison-fisher-cs}} $ | $
    \href{https://github.com/HarrisonFisher}{\underline{\faGithub \hspace{1pt} github.com/HarrisonFisher}}
\end{center}


%-----------EDUCATION-----------
  % East Bay
  % 36 CS Credits
  % 
  % May 12 2023

  % DVC
  % 20 CS Credits
  % 

  % Total: 126
  
  % {California State University East Bay, Hayward, CA}{Graduation Date: May 2023}

\section{Education}
  \resumeSubHeadingListStart

   \resumeSubheading
      {Diablo Valley College, Pleasant Hill, CA}{September 2025 - Present}
      {IT Essentials (A+), Microsoft Windows OS Essentials/Admin, and Introduction to Networks}{}
      
    \resumeSubheading
      % {California State University East Bay, Hayward, CA}{Graduation Date: August 2021 - May 2023}
      {California State University East Bay, Hayward, CA}{August 2021 - May 2023}
      {Bachelor of Science, Computer Science}{}

    \resumeSubheading
      {Diablo Valley College, Pleasant Hill, CA}{August 2018 - May 2021}
      {Associate  in Science, Computer Science}{}
  \resumeSubHeadingListEnd
  
%-----------PROGRAMMING SKILLS-----------
% trello
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C++, Lua, Java, Python, C, R, SQL, HTML, CSS, JavaScript, LISP, RISC-V, MIPS, MASM} \\
     \textbf{Developer Tools}{: Visual Studio Code, Visual Studio, CLion, Xcode, Eclipse IDE, R Studio, Git/GitHub} \\
     \textbf{Libraries/Frameworks}{: Microsoft Foundational Classes (MFC), Swing (Java)} \\
     \textbf{Spoken Languages}{: English (Native)} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    % \resumeSubheading
    %   {Admission Officer}{September 2020 -- Present}
    %   {St. Anford Office of Admission and Financial Aid}{Berkeley, California, United States}
    %   \resumeItemListStart
    %     \resumeItem{Randomly select \textbf{50,000} qualified applicants to reject each year unless the applicants is a legacy or pays millions to William Rick Singer.}
    %   \resumeItemListEnd
      
    % \resumeSubheading
    %   {Software Engineer Intern}{July 2021 -- September 2021}
    %   {Some Big Scientist Name Company}{Mars, Solar system}
    %   \resumeItemListStart
    %     \resumeItem{Developed a \textbf{long range rocket} that can send ants to Mars and cost as little as a house in Bay Area.}
    %     \resumeItem{Tried every kind of snacks offered at the office, including \textbf{La Tiao} (Spicy Bar).}
    %     \resumeItem{Finished \textbf{500} Leetcode questions while the manager was off duty.}
    %   \resumeItemListEnd

    \resumeSubheading
    {Freelance AI Trainer for Outlier.ai}{June 2024 -- Present}
    {Scale AI, Inc.}{Remote}
    \resumeItemListStart
      \resumeItem{Evaluate the ability of large language models to call API tools.}
      \resumeItem{Rate provided responses on tool choice, function, and parameter correctness.}
      \resumeItem{Indicate which response is better with a side-by-side rating and written justification.}
    \resumeItemListEnd

    % May 16th - Augh 5th 2022
    \resumeSubheading
    {Informatics Intern}{May 2022 -- August 2022}
    {Genentech, Inc.}{Remote}
    \resumeItemListStart
      \resumeItem{Contributed to the development of an open-source base-call-to-FASTQ converter to replace bcl2fastq2.}
      \resumeItem{Conducted research on the documentation and code for bcl2fastq by Illumina.}
      \resumeItem{Utilized an SSH server to access test data for the bcl2fastq program.}
      \resumeItem{Developed C++ code for parsing XML and CSV files from the test data.}
      \resumeItem{Implemented C++ code to manage various command-line arguments.}
      \resumeItem{Updated and built Docker images from Docker files.}
      % \resumeItem{Implemented a C/C++ software that can execute the conversion task in parallel}
      % \resumeItem{Extended this package to support alternative sequencing technologies, such as MGI sequencing}
    \resumeItemListEnd

    

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{Custom Gaming PC Builds and Troubleshooting}}{Ongoing}
        \resumeItemListStart
          \resumeItem{Built two high-performance gaming PCs}
          \resumeItem{Selected and assembled hardware components including CPU, GPU, motherboard, RAM, PSU, and cooling systems.}
          \resumeItem{Configured BIOS, installed OS, installed drivers.}
          \resumeItem{Independently diagnosed and resolved hardware/software issues during their use.}
        \resumeItemListEnd
        
      \resumeProjectHeading
          {\href{https://github.com/stephengpope/no-code-architects-toolkit}{\faGithub \hspace{1pt} \textbf{stephengpope/no-code-architects-toolkit}}\hspace{3pt}(Contributor \& Maintainer)}{May 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Save thousands of dollars on API subscriptions with this open source API built in Python using Flask.}
            \resumeItem{Works with Docker, Google Cloud Platform, Digital Ocean, and any system that hosts Docker.}
            \resumeItem{Easily replaces services like ChatGPT Whisper, Cloud Convert, Createomate, JSON2Video, PDF(dot)co, Placid, and OCodeKit.}
          \resumeItemListEnd
      \resumeSubheading
        {Software Engineering Project Team Lead}{January 2022 -- May 2022}
        {California State University East Bay}{Hayward, California, United States}
        \resumeItemListStart
          \resumeItem{Led a team in developing a Java-based chat system as part of a Software Engineering course, taking primary responsibility for implementing client-side functionalities and contributing to shared classes.}
          \resumeItem{Managed the project lifecycle to ensure timely completion and adherence to project requirements, from initial gathering to documentation.}
          \resumeItem{Facilitated communication and coordination among team members, incorporating feedback for iterative improvements.}
          \resumeItem{Engaged in regular meetings with the instructor acting as a client, providing updates and incorporating feedback.}
          \resumeItem{Utilized Git and GitHub for version control and effective collaboration.}
          \resumeItem{Demonstrated problem-solving skills and adeptness in troubleshooting technical issues.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd



%-------------------------------------------
\begin{center}
  \tiny 377 McAllister Dr., Benicia, CA 94510
\end{center}

\end{document}
